Portfolio prioritization of salmon conservation

### 2013-03-19 inst/examples/salmonport.Rmd
Add impl. error on fishing

o <- meta_sim(env_params = list(amplitude = .000000001, ang_frequency = 0.2, phase = 0, mean_value = 16), sigma_v = 0.01, n_pop = 10, stray_fraction = 0.00001, use_cache = FALSE)
o <- meta_sim(env_params = list(amplitude = .000000001, ang_frequency = 0.2, phase = 0, mean_value = 16), sigma_v = 0.1, n_pop = 10, stray_fraction = 0.00001, use_cache = FALSE)
#o<- meta_sim(b = rep(1000, 10), n_pop = 10)
plot_sim_ts(o, years_to_show = 60)
image(o$Est_b)
```

>>>>

o <- meta_sim(env_params = list(amplitude = .000000001, ang_frequency = 0.2, phase = 0, mean_value = 16), sigma_v = 0.01, n_pop = 10, stray_fraction = 0.00001, use_cache = FALSE)
o <- meta_sim(env_params = list(amplitude = 2.5, ang_frequency = 0.2, phase = 0, mean_value = 16), sigma_v = 0.00001, n_pop = 10, stray_fraction = 0.00001, use_cache = FALSE)
o <- meta_sim(env_params = list(amplitude = 2, ang_frequency = 0.2, phase = 0, mean_value = 16), sigma_v = 0.2, n_pop = 10, stray_fraction = 0.03, use_cache = FALSE)
#o<- meta_sim(b = rep(1000, 10), n_pop = 10)
plot_sim_ts(o, years_to_show = 60)
image(o$Est_b)
```
